\{\% include base\_path \%\}

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{itemize}
\tightlist
\item
  H.BSc. in Biology: Trent University, 2010-14
\item
  M.Sc. in Biology, Spec. Astrobiology: McMaster University, 2014-16
\item
  Ph.D.~in Biology: McMaster University, 2016-Current
\end{itemize}

\hypertarget{skills}{%
\section{Skills}\label{skills}}

Wet Lab: * General microbiology lab skills * Strain management *
Biosaftey level II * Library Preparation for Amplicon Sequencing * 16S +
ITS * qPCR \& PCR * Absolute \& relative quantitation assays * SYBER and
probe-based assays * Microdissection of Eukaryotic cells

Dry Lab: * Scripting languages * Bash * Python * Nextflow * Ruby (enough
to build this site) * R * Data managment (\texttt{tidyverse}) * Data
Visualization (\texttt{ggplot2}) * Multivariate analyses (PCA) *
Statistical modelling (\texttt{lme4}) * Spatial data analyses
(\texttt{sp}, \texttt{sf}, \texttt{gdistance}, \texttt{ResistanceGA}) *
Web scraping (\texttt{rvest}, \texttt{Rselenium}) * OTU datasets
(\texttt{phyloseq}) * Bioinformatics Skills * Variant Calling
(\texttt{gatk}, \texttt{freebayes}, etc.) * Genome alignment, assembly
(\texttt{bwa}, \texttt{velvet}, \texttt{SPades}, etc.) * Gene Annotation
* Copy number variants (\texttt{controlFREEC}) *
Metagenomic/Metabarcoding (\texttt{qiime2}) * Github project management
* LaTeX Typesetting (Overleaf \textless{}3)

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\{\% for post in site.publications \%\} \{\% include
archive-single-cv.html \%\} \{\% endfor \%\}

\hypertarget{awards-and-other-achievements}{%
\section{Awards and Other
Achievements}\label{awards-and-other-achievements}}

\begin{itemize}
\tightlist
\item
  Awarded Canadian Botany Association Luella K. Weresub Memorial Award
  for 2019 (\$500)
\item
  Recipient of the Outstanding Research Publication in Ecology and
  Evolution for the 2018-2019 academic year. (\$350)
\item
  Recipient of the Outstanding Leadership Award for the 2018-2019
  academic year. (\$350)
\item
  Recipient of a Service to the Department Award during the 2017-2018
  academic year. (\$350)
\item
  Awarded an Ontario Graduate Scholarship (OGS, \textasciitilde{} \$15
  000)

  \begin{itemize}
  \tightlist
  \item
    During the 2019-2020 academic year
  \item
    During the 2016-2017 academic year
  \end{itemize}
\item
  Lead organizer for Ontario Ethology, Ecology, and Evolution 2019
  conference.

  \begin{itemize}
  \tightlist
  \item
    The largest graduate student-organized biology/psychology event in
    Ontario
  \end{itemize}
\item
  IQAP Committee 2018, Graduate Student Representative

  \begin{itemize}
  \tightlist
  \item
    IQAP Learning Outcomes conducted a survey of Alumni and current
    students, analyzed responses, and summaries results to board of
    external reviewers.
  \end{itemize}
\item
  Co-President of the McMaster Biology Graduate Student Society, 2017 -
  2018 academic year

  \begin{itemize}
  \tightlist
  \item
    I coordinated social events for other Graduate Students and members
    of Faculty in the Biology department: Biology Graduate Research Day
    2018.
  \end{itemize}
\item
  SIAM Consulting 2018-current

  \begin{itemize}
  \tightlist
  \item
    An advisor for the McMaster chapter of the Society of Industrial and
    Applied Mathematics (SIAM).
  \item
    I advise other researchers with projects using bioinformatics tools
    in Unix, statistical analysis in R, and LaTex.
    https://siam.mcmaster.ca/consulting.html
  \end{itemize}
\item
  Overleaf Advisor (overleaf.com/advisors\#!members)
\end{itemize}
